Preprocess

### 2024-01-25 manuscript/manuscript.tex
Check code and run for reproducibility

For InterVA-5 and InSilicoVA, the standardized questionnaire data from the HEAL-SL EVA were first converted into 2016 World Health Organization (WHO) VA questionnaire revision 1.5.1 
\cite{dipasqualeReleaseODK20162016} Open Data Kit (ODK) format \cite{worldhealthorganizationODKVerbalAutopsy2022,nafundiODKCollectData2023}, followed by further conversion into OpenVA format \cite{liOpenVAToolkitVerbal2023} using the \verb|pyCrossVA| Python package \cite{thomasPycrossvaPrepareData}, and used as input for InterVA-5 and InSilicoVA. The \verb|Nsim| (number of iterations to run) parameter for InSilicoVA was set to 10,000, while the \verb|HIV| (level of prevalence of human immunodeficiency virus) and \verb|Malaria| (level of prevalence of Malaria) parameters were both set to \verb|'h'| (high).

>>>>

For InterVA-5 and InSilicoVA, the standardized questionnaire data from the HEAL-SL EVA were first converted into 2016 World Health Organization (WHO) VA questionnaire revision 1.5.1 
\cite{dipasqualeReleaseODK20162016} Open Data Kit (ODK) format \cite{worldhealthorganizationODKVerbalAutopsy2022,nafundiODKCollectData2023} consisting of 526 variables, followed by further conversion into OpenVA format \cite{liOpenVAToolkitVerbal2023} consisting of 353 variables \cite{byassInterVA5UserGuide2020} using the \verb|pyCrossVA| Python package \cite{thomasPycrossvaPrepareData}. The \verb|Nsim| (number of iterations to run) parameter for InSilicoVA was set to 10,000, while the \verb|HIV| (level of prevalence of human immunodeficiency virus) and \verb|Malaria| (level of prevalence of Malaria) parameters were both set to \verb|'h'| (high).

### 2024-01-25 src/plots.Rmd
Check code and run for reproducibility

```{r}
raw_df <- read_csv("../data/healsl_rd1to2_cod_v1.csv")
```

@@

```{r}
out <- reduce(metrics,
              function(x, y) left_join(x, y, by = "Model")
)
write_csv(out, "../data/healsl_rd1to2_metrics_v1.csv")
```

@@

# Save the plot
asplot
ggsave("../manuscript/fig-data-agesex.pdf", plot = asplot, dpi = 300)
```

@@

    # Save the plot
    print(earplot)
    ggsave(
        sprintf("../manuscript/fig-data-agerange-%s.pdf", a),
        plot = earplot,
        dpi = 300
    )
}
```

@@

    # Save the plot
    print(ecodplot)
    ggsave(
        sprintf("../manuscript/fig-data-cod-%s.pdf", a),
        plot = ecodplot,
        dpi = 300,
        width = if (a == "adult") 6 else NA,
        height = if (a == "adult") 8 else NA
    )
}
```

@@

# Save the plot
allplot
ggsave("../manuscript/fig-perf-allvsagree.pdf", plot = allplot, dpi = 300)
```

@@

# Save the plot
ageplot
ggsave("../manuscript/fig-perf-agegroup.pdf", plot = ageplot, dpi = 300)
```

@@

    # Save the plot
    print(sxplot)
    ggsave(
        sprintf("../manuscript/fig-perf-sex-%s.pdf", a),
        plot = sxplot,
        dpi = 300
    )
}
```

@@

    # Save the plot
    print(arplot)
    ggsave(
        sprintf("../manuscript/fig-perf-agerange-%s.pdf", a),
        plot = arplot,
        dpi = 300,
        width = if (a == "adult") 6 else if (a == "neo") 6 else NA,
        height = if (a == "adult") 8 else if (a == "neo") 2.5 else NA
    )
}
```

@@

    # Save the plot
    print(codplot)
    ggsave(
        sprintf("../manuscript/fig-perf-cod-%s.pdf", a),
        plot = codplot,
        dpi = 300,
        width = if (a == "adult") 8 else NA,
        height = if (a == "adult") 10 else NA
    )
}
```

>>>>

```{r}
raw_df <- read_csv("/data/healsl_rd1to2_cod_v1.csv")
```

@@

```{r}
out <- reduce(metrics,
              function(x, y) left_join(x, y, by = "Model")
)
write_csv(out, "/data/healsl_rd1to2_metrics_v1.csv")
```

@@

# Save the plot
asplot
ggsave("/manuscript/fig-data-agesex.pdf", plot = asplot, dpi = 300)
```

@@

    # Save the plot
    print(earplot)
    ggsave(
        sprintf("/manuscript/fig-data-agerange-%s.pdf", a),
        plot = earplot,
        dpi = 300
    )
}
```

@@

    # Save the plot
    print(ecodplot)
    ggsave(
        sprintf("/manuscript/fig-data-cod-%s.pdf", a),
        plot = ecodplot,
        dpi = 300,
        width = if (a == "adult") 6 else NA,
        height = if (a == "adult") 8 else NA
    )
}
```

@@

# Save the plot
allplot
ggsave("/manuscript/fig-perf-allvsagree.pdf", plot = allplot, dpi = 300)
```

@@

# Save the plot
ageplot
ggsave("/manuscript/fig-perf-agegroup.pdf", plot = ageplot, dpi = 300)
```

@@

    # Save the plot
    print(sxplot)
    ggsave(
        sprintf("/manuscript/fig-perf-sex-%s.pdf", a),
        plot = sxplot,
        dpi = 300
    )
}
```

@@

    # Save the plot
    print(arplot)
    ggsave(
        sprintf("/manuscript/fig-perf-agerange-%s.pdf", a),
        plot = arplot,
        dpi = 300,
        width = if (a == "adult") 6 else if (a == "neo") 6 else NA,
        height = if (a == "adult") 8 else if (a == "neo") 2.5 else NA
    )
}
```

@@

    # Save the plot
    print(codplot)
    ggsave(
        sprintf("/manuscript/fig-perf-cod-%s.pdf", a),
        plot = codplot,
        dpi = 300,
        width = if (a == "adult") 8 else NA,
        height = if (a == "adult") 10 else NA
    )
}
```

### 2024-01-25 src/preprocess.Rmd
Check code and run for reproducibility

        "../data/wva2016_icd10_v1.csv",

@@

    icd10_cghr10 = read_csv("../data/icd10_cghr10_v1.csv"),

@@

            "../tmp/healsl_rd1_adult_v1.csv",

@@

            "../tmp/healsl_rd2_adult_v1.csv",

@@

            "../tmp/healsl_rd1_child_v1.csv",

@@

            "../tmp/healsl_rd2_child_v1.csv",

@@

            "../tmp/healsl_rd1_neo_v1.csv",

@@

            "../tmp/healsl_rd2_neo_v1.csv",

@@

            "../tmp/healsl_rd1_rapid_chatgpt3_v1.csv",

@@

            "../tmp/healsl_rd2_rapid_chatgpt3_v1.csv",

@@

            "../tmp/healsl_rd1_rapid_chatgpt4_v1.csv",

@@

            "../tmp/healsl_rd2_rapid_chatgpt4_v1.csv",

@@

            "../tmp/healsl_rd1_rapid_insilicova_v1.csv",

@@

            "../tmp/healsl_rd2_rapid_insilicova_v1.csv",

@@

            "../tmp/healsl_rd1_rapid_interva5_v1.csv",

@@

            "../tmp/healsl_rd2_rapid_interva5_v1.csv",

@@

            "../tmp/healsl_rd1_adult_narrative_v1.csv",

@@

            "../tmp/healsl_rd1_child_narrative_v1.csv",

@@

            "../tmp/healsl_rd1_neo_narrative_v1.csv",

@@

            "../tmp/healsl_rd2_adult_narrative_v1.csv",

@@

            "../tmp/healsl_rd2_child_narrative_v1.csv",

@@

            "../tmp/healsl_rd2_neo_narrative_v1.csv",

@@

            "../tmp/healsl_rd1_who_adult_v1.csv",

@@

            "../tmp/healsl_rd1_who_child_v1.csv",

@@

            "../tmp/healsl_rd1_who_neo_v1.csv",

@@

            "../tmp/healsl_rd2_who_adult_v1.csv",

@@

            "../tmp/healsl_rd2_who_child_v1.csv",

@@

            "../tmp/healsl_rd2_who_neo_v1.csv",

@@

```{r}
write_csv(out, "../data/healsl_rd1to2_cod_v1.csv")
```

>>>>

        "data/wva2016_icd10_v1.csv",

@@

    icd10_cghr10 = read_csv("data/icd10_cghr10_v1.csv"),

@@

            "tmp/healsl_rd1_adult_v1.csv",

@@

            "tmp/healsl_rd2_adult_v1.csv",

@@

            "tmp/healsl_rd1_child_v1.csv",

@@

            "tmp/healsl_rd2_child_v1.csv",

@@

            "tmp/healsl_rd1_neo_v1.csv",

@@

            "tmp/healsl_rd2_neo_v1.csv",

@@

            "tmp/healsl_rd1_rapid_chatgpt3_v1.csv",

@@

            "tmp/healsl_rd2_rapid_chatgpt3_v1.csv",

@@

            "tmp/healsl_rd1_rapid_chatgpt4_v1.csv",

@@

            "tmp/healsl_rd2_rapid_chatgpt4_v1.csv",

@@

            "tmp/healsl_rd1_rapid_insilicova_v1.csv",

@@

            "tmp/healsl_rd2_rapid_insilicova_v1.csv",

@@

            "tmp/healsl_rd1_rapid_interva5_v1.csv",

@@

            "tmp/healsl_rd2_rapid_interva5_v1.csv",

@@

            "tmp/healsl_rd1_adult_narrative_v1.csv",

@@

            "tmp/healsl_rd1_child_narrative_v1.csv",

@@

            "tmp/healsl_rd1_neo_narrative_v1.csv",

@@

            "tmp/healsl_rd2_adult_narrative_v1.csv",

@@

            "tmp/healsl_rd2_child_narrative_v1.csv",

@@

            "tmp/healsl_rd2_neo_narrative_v1.csv",

@@

            "tmp/healsl_rd1_who_adult_v1.csv",

@@

            "tmp/healsl_rd1_who_child_v1.csv",

@@

            "tmp/healsl_rd1_who_neo_v1.csv",

@@

            "tmp/healsl_rd2_who_adult_v1.csv",

@@

            "tmp/healsl_rd2_who_child_v1.csv",

@@

            "tmp/healsl_rd2_who_neo_v1.csv",

@@

```{r}
write_csv(out, "data/healsl_rd1to2_cod_v1.csv")
```
